Macro Impacts

### 2016-08-05 Macro Impacts Revised.tex
Attenuated Energy

E_{\te{propagated}}&=\f{\lambda+2\mu}{K^2}2p_0^2(b^2f_1(a)-a^2f_1(b))^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}+\scr O(k_0^4)\,,\\

@@

>>>>

E_{\te{propagated}}&=\f{\lambda+2\mu}{K^2}2p_0^2(b^2f_1(b)-a^2f_1(a))^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}+\scr O(k_0^4)\,,\\

@@

Unfortunately, the above overestimate is too much of an overestimate. It is likely the best line of thinking to use the guessed wave-form. In this case, we have
P(\vec k) = \f{4\pi p_0}{k\cos\theta}\sin\p{\f{h}{2}k\cos\theta}
We may just want to do numerical integration. The problem is that these integrals oscillate rather quickly... Another idea is to simply drop all terms that are suppressed by some cutoff factor.
\section{Better Estimate}
The frequency distribution of the rays is to first order $\f{kb}{2}\ll 1$
P(\vec k) = \f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))
Indeed, since $b$ is on the order of $1\te{m}$, and the frequencies measurable to the lunar seismometers are at most $2\te{Hz}$, we have that $\f{bk}{2}\approx 10^{-3}\ll 1$. Now, the attenuated energy in this part of the spectrum goes as
\f{\lambda+2\mu}{K^2}\int\f{\diff^3k}{2\pi}P(\vec k)^2e^{-k\f{T}{Q}}
The energy in the range $[k_0,k_1]$ where $\f{k_1 b}{2}\ll 1$. is then
\notag E_{\te{attenuated}} =&\f{\lambda + 2\mu}{K^2}2p_0^2(b^2 f_1(b) - a^2 f_1(a))^2 \f{1}{T^2}e^{-\f{(k_0+k_1)(\I h Q+T)}{Q}} Q\p{-\p{e^{\I h k_0+\f{k_0T}{Q}} \notag -2e^{\I h(k_0+k_1)+\f{k_0 T}{Q}} \right.\right.\\&\left.\left.+ e^{\I h(k_0 + 2k_1) + \f{k_0 T}{Q}} - e^{\I h k_1 \notag + \f{k_1 T}{Q}} + 2 e^{\I h(k_0 + k_1) + \f{k_1 T}{Q}} - e^{\I h(2k_0 + k_1)+\f{k_1 T}{Q}}}T \right.\\&\left.- \I \notag e^{\f{(k_0+k_1)(\I h Q + T)}{Q}}h Q\p{\te{Ei}\ps{-\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{-\I h k_1 - \f{k_1 T}{Q}} + \te{Ei}\ps{\I h k_1 - \f{k_1 T}{Q}}   } \right.\\&\left.+ 2e^{\I h(k_0+k_1)} h \p{e^{\f{k_1 T}{Q}}(Q + k_0 T)\te{Si}\ps{h k_0} - e^{\f{k_0 T}{Q}}(Q + k_1 T)\te{Si}\ps{h k_1}}}\,.
We know that the energy in this range before attenuation is
E_{\te{detectable}} = \f{\lambda+2\mu}{K^2}2p_0^2(b^2f_1(b)-a^2f_1(a))^2\ps{-2k+k\cos(h k)+\f{\sin(h k)}{h}+h k^2\te{Si}(h k)}_{k=k_0}^{k_1}
What is the measurable attenuated energy in terms of the total deposited energy?
We need to pick a function $f$. A shock wave tends to be a right triangle, so let's pick the triangle from before. We then get
E_{\te{total}}=\f{\lambda+2\mu}{K^2}\f16 p_0^2 \pi\Delta r h(4 r_0+3\Delta r)\,,
f_1(x)=\f{-r_0}{2\Delta r}+\f{x}{3\Delta r}\,.
Hence, for $b = r_0+\Delta r$ and $a = r_0$, we have
b^2 f_1(b)-a^2f_1(a) = \f16\Delta r(3r_0+2\Delta r)\,.
The initial energy deposition is
E = \rho\sigma_Xv_X^2h\,.
Thus
2p_0^2\f{\lambda+2\mu}{K^2} =  \f{12}{\pi}\f{\rho\sigma_Xv_X^2}{\Delta r (4r_0+3\Delta r)}\,.
\notag E_{\te{attenuated}} =&\f{1}{3\pi}\f{\rho\sigma_Xv_X^2}{\Delta r (4r_0+3\Delta r)}\ps{ \Delta r(3r_0+2\Delta r)}^2 \f{1}{T^2}e^{-\f{(k_0+k_1)(\I h Q+T)}{Q}} Q\p{-\p{e^{\I h k_0+\f{k_0T}{Q}} \notag -2e^{\I h(k_0+k_1)+\f{k_0 T}{Q}} \right.\right.\\&\left.\left.+ e^{\I h(k_0 + 2k_1) + \f{k_0 T}{Q}} - e^{\I h k_1 \notag + \f{k_1 T}{Q}} + 2 e^{\I h(k_0 + k_1) + \f{k_1 T}{Q}} - e^{\I h(2k_0 + k_1)+\f{k_1 T}{Q}}}T \right.\\&\left.- \I \notag e^{\f{(k_0+k_1)(\I h Q + T)}{Q}}h Q\p{\te{Ei}\ps{-\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{-\I h k_1 - \f{k_1 T}{Q}} + \te{Ei}\ps{\I h k_1 - \f{k_1 T}{Q}}   } \right.\\&\left.+ 2e^{\I h(k_0+k_1)} h \p{e^{\f{k_1 T}{Q}}(Q + k_0 T)\te{Si}\ps{h k_0} - e^{\f{k_0 T}{Q}}(Q + k_1 T)\te{Si}\ps{h k_1}}}\,,\\
=&\f{1}{3\pi}\f{\rho\sigma_Xv_X^2\Delta r}{(4r_0+3\Delta r)}\ps{(3r_0+2\Delta r)}^2 \f{1}{T^2}e^{-\f{(k_0+k_1)(\I h Q+T)}{Q}} Q\p{-\p{e^{\I h k_0+\f{k_0T}{Q}} \notag -2e^{\I h(k_0+k_1)+\f{k_0 T}{Q}} \right.\right.\\&\left.\left.+ e^{\I h(k_0 + 2k_1) + \f{k_0 T}{Q}} - e^{\I h k_1 \notag + \f{k_1 T}{Q}} + 2 e^{\I h(k_0 + k_1) + \f{k_1 T}{Q}} - e^{\I h(2k_0 + k_1)+\f{k_1 T}{Q}}}T \right.\\&\left.- \I \notag e^{\f{(k_0+k_1)(\I h Q + T)}{Q}}h Q\p{\te{Ei}\ps{-\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{\I h k_0 - \f{k_0 T}{Q}} - \te{Ei}\ps{-\I h k_1 - \f{k_1 T}{Q}} + \te{Ei}\ps{\I h k_1 - \f{k_1 T}{Q}}   } \right.\\&\left.+ 2e^{\I h(k_0+k_1)} h \p{e^{\f{k_1 T}{Q}}(Q + k_0 T)\te{Si}\ps{h k_0} - e^{\f{k_0 T}{Q}}(Q + k_1 T)\te{Si}\ps{h k_1}}}\,.
Note, the bigger $r_0$ and $\Delta r$ are, the bigger $E_{\te{attenuated}}$ will be. A very generous over estimate is to say that $\Delta r = r_0 = 1\te{m}$. Another way to do this is as we did earlier, by starting the propagation once the wave has reached a certain pressure $\bar p \approx 10^8\te{Pa}$.
